Verifying Demonstrations

### 2017-09-20 intro.tex
Prepares contributions for later filling

In this paper, we combine the verifiability and privacy properties of 
electronic voting with location-proof systems to provide a verifiable 
participation count.
We can only provide a verifiable participation count for non-government 
protests:
In any pro-government protest we cannot prevent the government from doing a 
Sybil attack, since the government controls the identity system.

%In the case of the Korean demonstrations~\cite{2016DemonstrationsInSeoul}, this 
%was in one place during an entire day and then repeated for several weekends.
%In the case of the Women's Marches in the US~\cite{2017WomensMarchesInUS}, they
%were in several locations at the same time.

%\blockcquote{HowToEstimateCrowdSize}{%
%  Crowd size is also needed for media news reports and to historically record 
%  the event%
%}

>>>>

We propose a protocol which provides a way for protests to be securely verified.
Additionally, this verification system does not incur any additional risk to 
protesters' privacy than participating in the physical protest itself.

\dots
